High-Fidelity Counterfactual Explanations through Conformal Prediction

### 2023-04-27 notebooks/mnist.qmd

```{julia}
function pre_process(x; noise::Float32=0.03f0)
    ϵ = Float32.(randn(size(x)) * noise)
    x = @.(2 * x - 1) .+ ϵ
    return x
end
```

@@

```{julia}
# ECCCo:
λ=[0.5,0.1,0.5]
temp=0.5
η=0.01

@@

ces = Dict()
for (mod_name, mod) in model_dict
    ce = generate_counterfactual(
        x_factual, target, counterfactual_data, mod, eccco_generator; 
        decision_threshold=γ, max_iter=T,
        initialization=:identity,
        converge_when=:generator_conditions,
    )
    ces[mod_name] = ce
end
plt_order = sortperm(collect(keys(ces)))

@@

plts = []
for (_name,ce) in ces
    _x = CounterfactualExplanations.counterfactual(ce)
    _phat = target_probs(ce)
    _title = "$_name (p̂=$(round(_phat[1]; digits=3)))"
    plt = Plots.plot(
        convert2image(MNIST, reshape(_x,28,28)),
        axis=nothing, 
        size=(img_height, img_height),
        title=_title
    )
    plts = [plts..., plt]
end
plts = plts[plt_order]
plts = [p1, plts...]
plt = Plots.plot(plts...; size=(img_height*length(plts),img_height), layout=(1,length(plts)))
display(plt)
savefig(plt, joinpath(output_images_path, "mnist_eccco.png"))
```

>>>>

```{julia}
function pre_process(x; noise::Float32=0.03f0)
    ϵ = Float32.(randn(size(x)) * noise)
    x = @.(2 * x - 1) 
    x += ϵ
    return x
end
```

@@

```{julia}
plt_order = ["MLP", "MLP Ensemble", "JEM", "JEM Ensemble"]

# ECCCo:
λ=[0.5,0.1,0.5]
temp=0.5
η=0.01

@@

ces = Dict()
for (mod_name, mod) in model_dict
    ce = generate_counterfactual(
        x_factual, target, counterfactual_data, mod, eccco_generator; 
        decision_threshold=γ, max_iter=T,
        initialization=:identity,
        converge_when=:generator_conditions,
    )
    ces[mod_name] = ce
end
_plt_order = map(x -> findall(collect(keys(model_dict)) .== x)[1], plt_order)

@@

plts = []
for (_name,ce) in ces
    _x = CounterfactualExplanations.counterfactual(ce)
    _phat = target_probs(ce)
    _title = "$_name (p̂=$(round(_phat[1]; digits=3)))"
    plt = Plots.plot(
        convert2image(MNIST, reshape(_x,28,28)),
        axis=nothing, 
        size=(img_height, img_height),
        title=_title
    )
    plts = [plts..., plt]
end
plts = plts[_plt_order]
plts = [p1, plts...]
plt = Plots.plot(plts...; size=(img_height*length(plts),img_height), layout=(1,length(plts)))
display(plt)
savefig(plt, joinpath(output_images_path, "mnist_eccco.png"))
```
